---
title: "Computational Musicology: National Anthems of the world"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    theme: 
      version: 5
      bootswatch: minty
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tidyverse)
library(ggplot2)
library(spotifyr)
library(plotly)
library(compmus)
library(tidymodels)
europe <- get_playlist_audio_features("", "64wQFeHk3LgbPB2x6z3JNk")
asia <- get_playlist_audio_features("", "1YPj89O7XSAEwHSqQmquck")
americas <- get_playlist_audio_features("", "3col0xqk1N1zGenOzf5O34")

```

Visualizations {.storyboard data-icon="ion-stats-bars"}
=========================================
### Clustering theanthems of the different continents
#### Feature importance using random forest
```{r}
anthems <-
  bind_rows(
    europe |> mutate(playlist = "Europe") |> slice_head(n = 20),
    americas |> mutate(playlist = "Americas") |> slice_head(n = 20),
    asia |> mutate(playlist = "Asia") |> slice_head(n = 20)
  ) |> 
  add_audio_analysis()

anthems_features <-
  anthems |>  # For your portfolio, change this to the name of your corpus.
  mutate(
    playlist = factor(playlist),
    segments = map2(segments, key, compmus_c_transpose),
    pitches =
      map(
        segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      ),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = "mean",
      )
  ) |>
  mutate(pitches = map(pitches, compmus_normalise, "clr")) |>
  mutate_at(vars(pitches, timbre), map, bind_rows) |>
  unnest(cols = c(pitches, timbre))

anthems_recipe <-
  recipe(
    playlist ~
      danceability +
      energy +
      loudness +
      speechiness +
      acousticness +
      instrumentalness +
      liveness +
      valence +
      tempo +
      duration +
      C + `C#|Db` + D + `D#|Eb` +
      E + `F` + `F#|Gb` + G +
      `G#|Ab` + A + `A#|Bb` + B +
      c01 + c02 + c03 + c04 + c05 + c06 +
      c07 + c08 + c09 + c10 + c11 + c12,
    data = anthems_features           # Use the same name as the previous block.
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors())      # Converts to z-scores.
# step_range(all_predictors())    # Sets range to [0, 1].

anthem_cv <- anthems_features |> vfold_cv(5)

forest_model <-
  rand_forest() |>
  set_mode("classification") |> 
  set_engine("ranger", importance = "impurity")
anthem_forest <- 
  workflow() |> 
  add_recipe(anthems_recipe) |> 
  add_model(forest_model) |> 
  fit_resamples(
    anthem_cv, 
    control = control_resamples(save_pred = TRUE)
  )

plot_features <- workflow() |> 
  add_recipe(anthems_recipe) |> 
  add_model(forest_model) |> 
  fit(anthems_features) |> 
  pluck("fit", "fit", "fit") |>
  ranger::importance() |> 
  enframe() |> 
  mutate(name = fct_reorder(name, value)) |> 
  ggplot(aes(name, value)) + 
  geom_col() + 
  coord_flip() +
  theme_minimal() +
  labs(x = NULL, y = "Importance")

ggplotly(plot_features)

```

#### Important features

```{r}
plot_c <- anthems_features |>
  ggplot(aes(x = liveness, y = energy, colour = playlist, size = speechiness)) +
  geom_point(alpha = 0.8) +
  scale_color_viridis_d() +
  labs(
    x = "Liveness",
    y = "Energy",
    size = "Speechiness",
    colour = "Playlist"
  )

ggplotly(plot_c)
```
***
Text for clustering


### Tempogram of the Dutch national anthem

```{r}
graveola <- get_tidy_audio_analysis("30xbueSacPQZrRR7ZD6sST")

graveola_plot <- graveola |>
  tempogram(window_size = 8, hop_size = 1, cyclic = FALSE) |>
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic() +
  ggtitle('The Dutch National Anthem')

ggplotly(graveola_plot)

```
***

<iframe style="border-radius:12px" src="https://open.spotify.com/embed/track/30xbueSacPQZrRR7ZD6sST?utm_source=generator&theme=0" width="100%" height="152" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture" loading="lazy" data-external="1"></iframe>

### Histogram of tempi

```{r}
awards <-
  bind_rows(
    europe |> mutate(category = "Europe"),
    asia |> mutate(category = "Asia"),
    americas |> mutate(category = "Americas")
  )



cbPalette <- c("#8dd3c7",'#ffffb3','#bebada','#fb8072','#80b1d3','#fdb462','#b3de69','#fccde5')

barplotje <- awards %>% 
  ggplot(aes(x =tempo)) +
  geom_histogram(binwidth = 15, fill="darkgreen") +
  facet_wrap(~category) +
  ggtitle("Histogram of tempi per continent")+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(x = "Tempo (Bpm)", y = "Count") +
  theme_minimal() +
  scale_fill_manual(values=cbPalette)


ggplotly(barplotje, tooltip = c('count'))
```
***
The continents all have national anthems around 100 beats per minute. Europe has the most amount of national anthems that have a tempo with a beat per minute higher than 150.


### Chordogram of the most vs least danceable national anthem
#### Chordogram of the most danceable national anthem 

```{r}
#Chordogram------------------------------------------------------

circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


twenty_five <-
  get_tidy_audio_analysis("2Hplq9Qvud6B5PrNqUbxTV") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )

plot1 <- twenty_five |> 
  compmus_match_pitch_template(
    chord_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")+
  ggtitle("Chordogram of Kuwait")

plot1

```


#### Chordogram of the least danceable national anthem

```{r}
#Chordogram------------------------------------------------------

circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


twenty_five2 <-
  get_tidy_audio_analysis("4zZZT3WfGqyNhZnruVnNDV") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )

plot2 <- twenty_five2 |> 
  compmus_match_pitch_template(
    chord_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")+
  ggtitle("Chordogram of Aruba")

plot2
```
***

These Chordograms show two outliers of the from spotify defined variable danceabelity. The national anthem of Kuwait is the most danceable anthem in the world. The chordogram of this anthem illustrates the different chords over time. A change of chords is visible around 8 seconds, where Bb:min loses intensity and F:maj starts to gain intensity. At around 21 seconds this changes back to where it was in the beginning. The second chordogram is the chordogram of Aruba, the least danceable anthem in the world. This chordogram shows changes at around 15 seconds, 50 seconds, 70 seconds and 85 seconds. What is different between these chordograms is that the least danceable song has more changes in chords than that the most danceable song has which looks like it uses more or less the same chords. It could be because of this difference in the amount of changes that Spotify characterizes songs as more danceable or less danceable.


### Standard Deviation and mean in the national anthems
#### Tempo
```{r}
europe <-
  get_playlist_audio_features(
    "thesoundsofspotify",
    "64wQFeHk3LgbPB2x6z3JNk"
  ) |>
  slice(1:30) |>
  add_audio_analysis()
asia <-
  get_playlist_audio_features(
    "thesoundsofspotify",
    "1YPj89O7XSAEwHSqQmquck"
  ) |>
  slice(1:30) |>
  add_audio_analysis()
americas <-
  get_playlist_audio_features(
    "thesoundsofspotify",
    "3col0xqk1N1zGenOzf5O34"
  ) |>
  slice(1:30) |>
  add_audio_analysis()



jazz <-
  europe |>
  mutate(genre = "Europe") |>
  bind_rows(americas |> mutate(genre = "Americas"), asia |> mutate(genre = "Asia"))


jazz |>
  mutate(
    sections =
      map(
        sections,                                    # sections or segments
        summarise_at,
        vars(tempo, loudness, duration),             # features of interest
        list(section_mean = mean, section_sd = sd)   # aggregation functions
      )
  ) |>
  unnest(sections) |>
  ggplot(
    aes(
      x = tempo,
      y = tempo_section_sd,
      colour = genre,
      alpha = loudness
    )
  ) +
  geom_point(aes(size = duration / 60)) +
  geom_rug() +
  theme_minimal() +
  ylim(0, 5) +
  labs(
    x = "Mean Tempo (bpm)",
    y = "Standard Deviation Tempo",
    colour = "Continent",
    size = "Duration (min)",
    alpha = "Volume (dBFS)"
  )
```

#### Timbre
```{r}
jazzp <-jazz |>
  mutate(
    timbre =
      map(
        segments,
        compmus_summarise,
        timbre,
        method = "mean"
      )
  ) |>
  select(genre, timbre) |>
  compmus_gather_timbre() |>
  ggplot(aes(x = basis, y = value, fill = genre)) +
  geom_violin() +
  scale_fill_viridis_d(direction = -1, option='C') +
  labs(x = "Spotify Timbre Coefficients", y = "", fill = "Continent")


ggplotly(jazzp)

```
***
The Tempo plot shows the standard deviation of the tempo variable from spotify and its mean Tempo in beats per minute. From this plot it can be concluded that the mean tempo of the national anthems in Asia are the lowest. The standard Deviation of Europe seem to be the highest. The national anthems of the American continent have the longest duration.

In the second figure, the Timbre of the three continents are plotted. Overall, most of the timbre coefficients seem to be the same between the three continents. Coefficient c1, c2 and c3 however coud be a marker that distinguishes the European continent from the rest with slight changes in its shape.

### Histogram of Keys {data-commentary-width=400}

```{r}

awards <-
  bind_rows(
    europe |> mutate(category = "Europe"),
    asia |> mutate(category = "Asia"),
    americas |> mutate(category = "Americas")
  )



cbPalette <- c("#8dd3c7",'#ffffb3','#bebada','#fb8072','#80b1d3','#fdb462','#b3de69','#fccde5')

barplotje <- awards %>% 
  ggplot(aes(x = key_name, fill=key_name)) +
  geom_bar() +
  facet_wrap(~category) +
  ggtitle("Histogram of Keys per continent")+
  scale_fill_manual(values=cbPalette) +
  theme(plot.title = element_text(hjust = 0.5))+
  labs(x = "Key name", y = "Count")


ggplotly(barplotje, tooltip = c('count'))
```
***

The histogram of the American national anthems shows a high count of the key A#. The keys C# and D are missing in the histogram.
The histogram of the European continent has the most amount of A# keys and is the only continent missing the key C.
The national anthems of the continent of Asia have the most amount of different keys and the occurences of each key are more similar.

### Similarity Matrix
#### Timbre

```{r}
# Cepstrograms
bzt <-
  get_tidy_audio_analysis("50Ex1WYMkbe4mwdroVdLFP") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )


bzt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()+
  ggtitle("Timbre")+
  theme(plot.title = element_text(hjust = 0.5))


# SELF SIMILARITY MATRIX
bzt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")+
  ggtitle("Timbre")+
  theme(plot.title = element_text(hjust = 0.5))
```

#### Chroma

```{r}

bzt <-
  get_tidy_audio_analysis("50Ex1WYMkbe4mwdroVdLFP") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )



bzt |>
  mutate(pitches = map(pitches, compmus_normalise, "chebyshev")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_minimal() +
  scale_fill_viridis_c()+
  ggtitle("Chroma")+
  theme(plot.title = element_text(hjust = 0.5))





# SELF SIMILARITY MATRIX
bzt |>
  compmus_self_similarity(pitches, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "") +
  ggtitle("Chroma")+
  theme(plot.title = element_text(hjust = 0.5))
```

***

In this section, the chroma and timbre of the Chinese National Anthem are compared.
The first plots show the timbre changes which are mostly present on the c3 level. When listening to the song the timbre seems to correlate with the sounds of the trumpets. At around 6 seconds there is a small dip visible and at around 21 seconds there is a gap which align with the sound of the trumpets in the song.

The chromagram shows that the song is mostly grounded by B, G, D. Like the cepstrogram that shows the timbre, at around 21 seconds there is a clear gap visible, where D gets a lower magnitude. The magnitude of G and B get bigger around that time.



### Instrumentalness vs danceability

#### Instrumentalness vs danceability

```{r}

awards <-
  bind_rows(
    europe |> mutate(category = "Europe"),
    asia |> mutate(category = "Asia"),
    americas |> mutate(category = "Americas")
  )



plot1 <- 
awards |>                    # Start with awards.
  mutate(
    mode = ifelse(mode == 0, "Minor", "Major")
  ) |>
  ggplot(                     # Set up the plot.
    aes(
      x = instrumentalness,
      y = danceability,
      size = energy,
      colour = mode,
      text = track.name
    )
  ) +
  geom_point() +              # Scatter plot.
  geom_rug(linewidth = 0.1) + # Add 'fringes' to show data distribution.
  
  facet_wrap(~ category) +    # Separate charts per playlist.
  scale_x_continuous(         # Fine-tune the x axis.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),   # Use grid-lines for quadrants only.
    minor_breaks = NULL       # Remove 'minor' grid-lines.
  ) +
  scale_y_continuous(         # Fine-tune the y axis in the same way.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_brewer(        # Use the Color Brewer to choose a palette.
    type = "qual",            # Qualitative set.
    palette = "Pastel2"        # Name of the palette is 'Paired'.
  ) +
  scale_size_continuous(      # Fine-tune the sizes of each point.
    trans = "exp",            # Use an exp transformation to emphasise loud.
    guide = "none"            # Remove the legend for size.
  ) +
  theme_light() +             # Use a simpler theme.
  labs(                       # Make the titles nice.
    x = "Instrumentalness",
    y = "Dancebility",
    colour = "Mode"
  ) 


ggplotly(plot1)

```
***

This plot shows the danceability and the instrumentalness of the national anthems around the world. The size of the data points indicates the level of energy. The color illustrates whether or not the data point is in Minor or Major. From this plot, the american continent has the most instrumentalness in their national anthems. The most danceable national anthem is in Asia, Kuwait has a danceability of 0.8760.

### Energy vs Valence
#### Energy vs Valence
```{r}
awards <-
  bind_rows(
    europe |> mutate(category = "Europe"),
    asia |> mutate(category = "Asia"),
    americas |> mutate(category = "Americas")
  )



plotje <- awards |>                    # Start with awards.
  mutate(
    mode = ifelse(mode == 0, "Minor", "Major")
  ) |>
  ggplot(                     # Set up the plot.
    aes(
      x = valence,
      y = energy,
      size = loudness,
      colour = mode,
      text = track.name
    )
  ) +
  geom_point() +              # Scatter plot.
  geom_rug(linewidth = 0.1) + # Add 'fringes' to show data distribution.
  
  facet_wrap(~ category) +    # Separate charts per playlist.
  scale_x_continuous(         # Fine-tune the x axis.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),   # Use grid-lines for quadrants only.
    minor_breaks = NULL       # Remove 'minor' grid-lines.
  ) +
  scale_y_continuous(         # Fine-tune the y axis in the same way.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_brewer(        # Use the Color Brewer to choose a palette.
    type = "qual",            # Qualitative set.
    palette = "Pastel1"        # Name of the palette is 'Paired'.
  ) +
  scale_size_continuous(      # Fine-tune the sizes of each point.
    trans = "exp",            # Use an exp transformation to emphasise loud.
    guide = "none"            # Remove the legend for size.
  ) +
  theme_minimal() +             # Use a simpler theme.
  labs(                       # Make the titles nice.
    x = "Valence",
    y = "Energy",
    colour = "Mode"
  )

ggplotly(plotje)
```

***

This plots compare the Valence and Energy of each country within the playlists. For the american continent, most countries are clearly centered around 0.5 Valence. All the countries have an Energy of 0.5 and are in Major. The country that has the loudest national anthem is Canada with a loudness of 8.10e-5. The country national anthem with the highest Energy is that of the United States Virgin Islands with an energy of 0.48. In Asia, the national anthems are more spread out between the different values of Valence. Most countries have a Valence greater than 0.5. Compared between the other continents, Asia has the loudest national anthems where China has a loudness of 1.94e-4. Also, two countries have an Energy level above 0.5, Qatar with an Energy level of 0.5710 and Kuwait with a level of 0.5760. Europe has the most national anthems in Minor and it seems that most countries also have a national anthem with a Valence smaller than 0.5.


### Chromagram of the loudest national anthem in the world
#### Chromagram China

``` {r}
china_chroma <-
  get_tidy_audio_analysis("50Ex1WYMkbe4mwdroVdLFP") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

china_chroma |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_minimal() +
  scale_fill_viridis_c()

```

***




The chromagram shows a lot of repetitive G, D and B.


Corpus {data-icon="ion-ios-musical-notes"}
=========================================

Column {data-width=600}
-------------------------------------

### Introduction

The corpus that is used in my analysis consists out of all the national anthems of the world. The aim of this corpus is to analyze what musical characteristics of a song make it a national anthem. I find it interesting to see how one song can become so nationally known and rooted in a country. Within the corpus the music therefore all share the common factor that it is the national anthem of a country. One interesting aspect to consider is the geographical and cultural influences of national anthems to see if countries that are close together also share similarities of the same style in their national anthems. Another point of comparison could be the year that the national anthem song has been composed to see if it has any impact on the style of the national anthem compared to other countries that were composed in the same time period.

Typical national anthems are hard to define but one national anthem that stands out from the rest is the one from Nepal which anthem was introduced relatively recently and therefore uses more modern instruments distinguishing it from most older anthems.

It is important to note that the corpus is representative of all the national anthems of today, however, many national anthems have changed over time since their original composition. This can be seen as a limitation of the analysis, as it does not account for the historical evolution of national anthems. Nevertheless, this corpus offers a wealth of information about the musical characteristics of national anthems and is still able to provide a strong representation of the cultural heritage of a country.

Column {data-width=400}
-------------------------------------
    
### Corpus

<iframe style="border-radius:12px" src="https://open.spotify.com/embed/playlist/64wQFeHk3LgbPB2x6z3JNk?utm_source=generator&theme=0" width="100%" height="152" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture" loading="lazy" data-external="1"></iframe>

<iframe style="border-radius:12px" src="https://open.spotify.com/embed/playlist/3col0xqk1N1zGenOzf5O34?utm_source=generator&theme=0" width="100%" height="152" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture" loading="lazy" data-external="1"></iframe>

<iframe style="border-radius:12px" src="https://open.spotify.com/embed/playlist/1YPj89O7XSAEwHSqQmquck?utm_source=generator&theme=0" width="100%" height="152" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture" loading="lazy" data-external="1"></iframe>


Conclusions {data-icon="ion-document"}
=========================================
### Conclusions

```{r}


```

